---
title: "Day3_2"
format: html
editor: visual
---

####################Graphical Data Representation######################

Bar Plot

```{r}
setwd("E:/R/Datasets/")
cars93 <- read.csv("Cars93.csv")

a <- c(45,20,14)
b <- c(40,20,10)
barplot(a) #Basic, crude bar graphs

```

More than 1 column :

```{r}
ab <- rbind(a,b) #Binding a and b as rows in dataframe
barplot(ab)#Plotting A and B crudely
```

'beside' stacks them side by side 'col' will specify the color for the bars

Setting the bar colors to red and blue

```{r}
barplot(ab, beside=T, col=c("red","blue"))
```

Making a barplot on the frequency table of Types col in cars93 dataset :

```{r}
table(cars93$Type) |> barplot()

```

Now bar graph on 2 different columns

```{r}
table(cars93$Type, cars93$Origin) |> barplot(,beside=T)

```

If we want to provide a title to the main graph :

```{r}
table(cars93$Type, cars93$Origin) |> barplot(,beside=T,main="Car Types")

```

                    -------------HISTOGRAM----------------

```{r}
hist(cars93$Price, breaks=10) #Breaks are where the class interval is present
```

Class intervals should have equal width 
Class intervals are also known as Bins

Histograms have continuous scale at x axis so we cant shuffle Judge breaks correctly, too many breaks can screw up the data

```{r}
setwd("E:/R/Datasets/")
d <- read.csv2("Diamonds.csv")
hist(d$price, breaks=10,main = "Diamond Pricing", col=colors()[45]) #Breaks are where the class interval is present
colors()
```

Gives you all the colors in R You can specify colors()\[<number>\] to get the colors according to the number assigned to the color

                                ####BOX PLOT######
                                
Also known as Box and Whisker plot which are the two lines above and below the box

Gap between FIrst and 3rd Quartile is called Inter Quartile Range (IQR) In boxplot we only plot quartiles #Any data point that is 1.5IQR away from the edge of Box Plot it is tagged as Outlier

Outliers are extreme Observations that need to be tracked, more the variation more the outliers

```{r}
boxplot(cars93$Price) #Some outliers
boxplot(d$price)      #Many Outliers

boxplot(cars93$RPM) #No outliers

boxplot(d$depth) #Too many outliers
```

If we want to do boxplots for one col related to another col(Like group by)

```{r}
boxplot(cars93$Price ~ cars93$Type) #Price for every category
boxplot(d$depth ~ d$cut)

```

IF we want to change the scale it is ylim for y axis and xlim for xaxis

                      ###########SCATTERPLOT##########
                      
                      
Pch stands for Plotting Character, its the legend that marks a data point
Col for which color for the pch
```{r}
plot(cars93$Price,cars93$MPG.city)

plot(cars93$Price,cars93$MPG.city,pch=18, col ="green")

```

xlab = Xlabel
ylab = Ylabel
main=Name of the graph

```{r}
plot(cars93$Price,cars93$MPG.city,pch=18, col ="green", xlab="Car Price", ylab="Miles per Gallon",
     main="Scatter")

```
                          ########LINE PLOT###########

For timeseries based graphs X axis should be time
WHenever we plot against time its better to plot it as a linegraph


```{r}
setwd("E:/R/Datasets/")
gas <- read.csv("Gasoline.csv")
plot(gas$Week, gas$Sales, type='l') #Type = l for lineplot
plot(gas$Week, gas$Sales, type='b')#Type = b for lineplot and show the data points
```
                            ####DENSITY PLOT#####

Like histogram, but smoothened
Call density function on the data and then use Plot()


```{r}
cars93$Price |> density() |> plot()
```
OR

```{r}
plot(density(cars93$Price))
```
#--------------------------------------------------------------------------------------#
                               #####################
                               #      GGPLOT2      #
                               #####################
                               
                               
                               

For ggplot2, use function ggplot, specify the dataframe, then function aes[AESTHETIC] within it
to specify what is gonna be x axis and y axis and then 
USE "+" operator and pass the relevant plot function

geom_point() for scatterplot

```{r}
library(ggplot2)
setwd("E:/R/Datasets/")
sal <- read.csv("Salaries.csv", stringsAsFactors = T)
ggplot(data=sal, aes(x=yrs.service,y=salary)) + geom_point()

```

If values correspond to specific groups/ranks/columns we can specify separate colors for them
For rank

```{r}
ggplot(data=sal, aes(x=yrs.service,y=salary,color=rank)) + geom_point()

```

For Gender

```{r}
ggplot(data=sal, aes(x=yrs.service,y=salary,color=sex)) + geom_point()
```



                               